2019 Draft Prep

### 2019-03-22 draftPrep.Rmd
Work in progress switching to latest projections

##### Batters
(@) Runs (R)
(@) Hits (H)
(@) Home runs (HR)
(@) Runs Batted In (RBI)
(@) Stolen Bases (SB)
(@) Walks (BB)
(@) Strikeouts (SO/K)
(@) On-Base Percentage (OBP)
(@) On-Base Plus Slugging (OPS)
(@) \*Errors (E)

##### Pitchers
(@) Saves (SV)
(@) Strikeouts (SO/K)
(@) Holds (HLD)
(@) Earned Run Average (ERA)
(@) Walks+Hits per Inning (WHIP)
(@) \*No Hitters (NH)
(@) \*Quality Starts (QS)
(@) \*Blown Saves (BS)
(@) \*Complete Games (CG)
(@) \*Shut outs (SHO)

Categories marked with an asterisk (\*) are not inluded in projection data.

@@

(@) Batter projections tend to be more accurate than pitchers
(@) I tend to ride the waiver wire for starting pitching to take advantage of two-start weeks in an effort to find quality starts
(@) Since more batting categories are projected than pitching categories, I tend to put more emphasis on getting hitters early in drafts

# Data Set
```{r importFangraphs, include=FALSE}
fangraphs_pitchers <- "data/fangraphs_pitchers.Rds"
fangraphs_batters <- "data/fangraphs_batters.Rds"
pitchers_file <- "data/depthChartProjections_pitchers_20190308.csv"
batters_file <- "data/depthChartProjections_batters_20190308.csv"

if (file.exists(fangraphs_pitchers) && file.exists(fangraphs_batters)) {
  pitchers <- readRDS(fangraphs_pitchers)
  batters <- readRDS(fangraphs_batters)
} else {
  if (!file.exists(pitchers_file) || !file.exists(batters_file)) {
  stop("Couldn't find fangraphs export data in the data folder")
}

  pitchers <- pitchers_file %>%
    read_csv() %>%
    unique() %>%
    select(playerid, 
           Name, 
           Team,
           ADP,
           IP,
           SV:ERA,
           SO,
           WHIP) %>%
    mutate(type = "pitcher")

  batters <- batters_file %>%
    read_csv() %>%
    unique() %>%
    select(playerid,
           Name,
           Team,
           ADP,
           PA,
           H,
           HR:SO,
           SB,
           OBP,
           OPS) %>%
    mutate(type = "batter")

@@

  batters <- fangraphs %>%
    filter(type="batter") %>%
    select(-type)

  pitchers <- fangraphs %>%
    filter(type="pitcher") %>%
    select(-type)

  batters %>% saveRDS(fangraphs_batters)
  pitchers %>% saveRDS(fangraphs_pitchers)
}

rm(c(fangraphs_pitchers, fangraphs_batters, pitchers_file, batters_file, fangraphs))
```

@@

>>>>

##### Batters
- Runs (R)
- Hits (H)
- Home runs (HR)
- Runs Batted In (RBI)
- Stolen Bases (SB)
- Walks (BB)
- Strikeouts (SO/K)
- On-Base Percentage (OBP)
- On-Base Plus Slugging (OPS)
- \*Errors (E)

##### Pitchers
- Saves (SV)
- Strikeouts (SO/K)
- Holds (HLD)
- Earned Run Average (ERA)
- Walks+Hits per Inning (WHIP)
- \*No Hitters (NH)
- \*Quality Starts (QS)
- \*Blown Saves (BS)
- \*Complete Games (CG)
- \*Shut outs (SHO)

*Categories marked with an asterisk (\*) are not inluded in projection data.*

@@

1. Batter projections tend to be more accurate than pitchers
2. I tend to ride the waiver wire for starting pitching to take advantage of two-start weeks in an effort to find quality starts
3. Since more batting categories are projected than pitching categories, I tend to put more emphasis on getting hitters early in drafts

# Data Set
```{r importFangraphs, include=FALSE}
fangraphs_pitchers <- "data/fangraphs_pitchers.Rds"
fangraphs_batters <- "data/fangraphs_batters.Rds"
pitchers_file <- "data/depthChartProjections_pitchers_20190321.csv"
batters_file <- "data/depthChartProjections_batters_20190321.csv"

if (!file.exists(pitchers_file) || !file.exists(batters_file)) {
  stop("Couldn't find fangraphs export data in the data folder")
}

pitchers <- 
  pitchers_file %>%
  read_csv() %>%
  unique() %>% 
  mutate(type = "pitcher")

batters <- batters_file %>%
  read_csv() %>%
  unique() %>%
  mutate(type = "batter")

@@

batters <- fangraphs %>%
  filter(type=="batter") %>%
  select(playerid,
         Name,
         Team,
         ADP,
         PA,
         H,
         HR:SO,
         SB,
         OBP,
         OPS)

pitchers <- fangraphs %>%
  filter(type=="pitcher") %>%
  select(playerid,
         Name,
         Team,
         ADP,
         IP,
         SV:ERA,
         SO,
         WHIP)

batters %>% saveRDS(fangraphs_batters)
pitchers %>% saveRDS(fangraphs_pitchers)

suppressWarnings(
  rm(fangraphs_pitchers, fangraphs_batters, pitchers_file, batters_file) 
)
```

@@

```{r}
players_master <- fangraphs %>%
  full_join(yahoo_players, by = c("Name" = "name.full")) %>%
  filter(!is.na(ADP))

players_master %>% 
  mutate(orphan = is.na(display_position) & is.na(positions)) %>%
  filter(orphan) -> orphans

if (!is.na(orphans) && nrow(orphans) > 0) {
  stop(paste0("Join resulted in ",nrow(orphans)," orphaned players"))
}

orphans %>% select(Name)
fangraphs %>% filter(grepl("Genesis",Name))
yahoo_players %>% filter(grepl("Cabrera",name.full))
```
